BurgerMax Presents: OpenAdcess

### 2017-02-28 digital-library.tex
Took a stab at the intro
Related work

\section{Digital Library}
Shady websites have long managed to monetize content downloads.
To provide free access to papers, we can follow their model by making the
following changes.

\subsection{Fake Download Buttons}

@@

\subsection{Rate Limited Free Downloads}
Free download sites figured out long ago that you can make people pay for an
otherwise free product by making the process of obtaining that free product
difficult.
Therefore, we will split our digital library downloads into two tiers, the free
tier and the \premium tier.

>>>>

\section{Digital Library}
\label{sec:lib}
Shady websites have long managed to monetize content downloads.
To provide free access to papers, we can follow their model by making the
following changes.

\subsection{Fake Download Buttons}
\label{sec:fake}

@@

\subsection{Rate Limited Free Downloads}
\label{sec:limit}
Free download sites figured out long ago that you can make people pay for an
otherwise free product by making the process of obtaining that free product
difficult.
Therefore, we will split our digital library downloads into two tiers, the free
tier and the \premium tier.

### 2017-02-28 paper-sponsorships.tex
Took a stab at the intro
Related work

\section{Paper Sponsorships}
In addition to ads on our Digital Library, we will also be adding
advertisements to the papers themselves.
These advertisements will come in many forms, including standard banner
advertisements as well as the increasingly popular native advertisement.

@@

% TODO: Reference this:
% http://www.cs.utexas.edu/users/EWD/transcriptions/EWD07xx/EWD743.html
\subsection{Branded mathematical objects}
We believe there has been a missed opportunity in the field of mathematics to
increase brand awareness.
Therefore, we propose branding mathematical objects by associating every single
set with an individual brand.
Brands can purchase large collections of sets at a discount.
While most sets are cheap, some more famous sets will sell for more to reflect
the higher market value, similar to domain names.
Thus, ACM will create an ICANN equivalent for these sets.

>>>>

\section{Paper Sponsorships}
\label{sec:sponsors}
In addition to ads on our Digital Library, we will also be adding
advertisements to the papers themselves.
These advertisements will come in many forms, including standard banner
advertisements as well as the increasingly popular native advertisement.

@@

% TODO: Reference this:
% http://www.cs.utexas.edu/users/EWD/transcriptions/EWD07xx/EWD743.html
\subsection{Branded mathematical objects}
\label{sec:brands}
We believe there has been a missed opportunity in the field of mathematics to
increase brand awareness.
Therefore, we propose branding mathematical objects by associating every single
set with an individual brand.
Brands can purchase large collections of sets at a discount.
While most sets are cheap, some more famous sets will sell for more to reflect
the higher market value, similar to domain names.
Thus, ACM will create an ICANN equivalent for these sets.
